Using simulation to optimize the sampling design of fisheries-independent trawl surveys

### 2019-02-07 analysis/paper/sim_survey_paper.Rmd
Improve font size of error_surface figure and improve docx template

export_plot(p, file = "analysis/paper/figures/plot_error_surface.png", width = 1250, height = 400)

@@

```{r rmse-surface, fig.cap = "- Surface plots of RMSE from an array of surveys with different sampling protocol. Panels represent surveys with different set densities ($D_{sets}$), x-axes represent the maximum sampling effort of lengths per set ($M_{lengths}$), and y-axes represent the maximum number of ages to collect per length group (M_{ages}). This plot is a facet of plots produced by `plot_error_surface` when supplied results from `test_surveys`. Note that the z-axes scales are different across the facets."}

>>>>

export_plot(p, file = "analysis/paper/figures/plot_error_surface.png", width = 990, height = 270)

@@

```{r rmse-surface, fig.cap = "- Surface plots of RMSE from an array of surveys with different sampling protocol. Panels represent surveys with different set densities ($D_{sets}$), x-axes represent the maximum sampling effort of lengths per set ($M_{lengths}$), and y-axes represent the maximum number of ages to collect per length group ($M_{ages}$). This plot is a facet of plots produced by `plot_error_surface` when supplied results from `test_surveys`. Note that the z-axes scales are different across the facets."}
